\Rpackage{MSnbase}: labelled MS2 data pre-processing, visualisation and quantification.

### 2013-03-22 inst/doc/MSnbase-demo/MSnbase-demo.Rnw
Merge branch 'master' into local-hedgehog
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@74588 bc3139a8-67e5-0310-9ffc-ced21a209358
Merge branch 'master' into local-hedgehog
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@74673 bc3139a8-67e5-0310-9ffc-ced21a209358

<<environment, cache=FALSE, echo=FALSE>>=
suppressPackageStartupMessages(library("MSnbase"))
suppressPackageStartupMessages(library("zoo"))
if (.Platform$OS.type != "windows")
  suppressPackageStartupMessages(library("doMC"))
suppressPackageStartupMessages(library("multicore"))
library("grid")
library("reshape2")
@

@@

A \Robject{MSnSet} object is meant to be compatible with further downstream 
packages for data normalisation and statistical analysis. There is also a 
\Rfunction{normalise} method for expression sets. The method takes and instance 
of class \Robject{MSnSet} as first argument, and a character to describe the 
\Robject{method} to be used:

@@

>>>>

<<environment, cache=FALSE, echo=FALSE>>=
suppressPackageStartupMessages(library("MSnbase"))
suppressPackageStartupMessages(library("zoo"))
if (.Platform$OS.type != "windows")
  suppressPackageStartupMessages(require("doMC"))
suppressPackageStartupMessages(require("multicore"))
library("grid")
library("reshape2")
@

@@

A \Robject{MSnSet} object is meant to be compatible with further downstream 
packages for data normalisation and statistical analysis. There is also a 
\Rfunction{normalise} (also available as \Rfunction{normalize}) 
method for expression sets. The method takes and instance 
of class \Robject{MSnSet} as first argument, and a character to describe the 
\Robject{method} to be used:

@@

See \Rfunction{?normalise} for more methods. A \Rfunction{scale} method for \Robject{MSnSet} 
instances, that relies on the \Rfunction{base::scale} function.
